---
title: "mydas"
subtitle: "Elasticity Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Laurence Kell"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{FLife-WKLife}
  %\VignetteEncoding{UTF-8}
bibliography: refs.bib
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =!TRUE,
               echo      =TRUE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =FALSE,
               fig.height=6,
               fig.width =8)

options(digits=3)
iFig=0
```


## Load Libraries
```{r}
library(FLCore)
library(ggplotFL)
library(FLasher)
library(FLBRP)

library(FLife)
library(mydas)
```

# Life history parameters


```{r}
par=FLPar(c(linf=59.1,  k=0.28, t0=-0.4, a=0.01111,
            b   =3.15,a50=4.0, l50=43.25),units="NA")
par=lhPar(par)
```

```{r, refpts}
fn<-function(x) log(refpts(lhEql(x,refpts="msy"))[,c("harvest","ssb","yield"),drop=T])
res=jacobian(fn,par)

dimnames(res)=list(c("harvest","ssb","yield"),dimnames(par)$params)
res
```

```{r, lopt}
fn<-function(x) log(lopt(x)[,drop=T])
res=jacobian(fn,par[c("linf","k","t0","a","b","m1","m2","m3")])

dimnames(res)=list("lopt",c("linf","k","t0","a","b","m1","m2","m3"))
res
```

**Figure `r iFig=iFig+1; iFig`** Equilibrium curves.


## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLBRP:  `r packageVersion('FLBRP')`
* FLife:  `r packageVersion('FLife')`
* mydas:  `r packageVersion('mydas')`
* **Compiled**: `r date()`

## Author information

**Laurence KELL**. laurie.kell.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}


